Composition-climate paper

### 2015-07-06 Composition_Ecology.Rmd
Changing the code so that `source`d files live as functions, reducing the number of global variables.
Added Jin reference for the NLCD reference.

Working on the Hellinger code, there are some problems right now witht he PLS data not getting added properly.

Clearning out some stuff from `get_pls`.

Temporarily added the `GSA_Presentation_diagrams` so I can pull diagrams from there into the paper.

Modifying `ordination_plot` so that it works a bit more effectively.
Working on the final plots for the paper.  Adding in some text results.
Added `analogue` to the setup file, allowing us to use th

source('R/Setup_R.R')
source('R/load_climate.R') # gives then.clim & now.clim
source('R/load_veg.R')

@@

loss_plots <- loss_plot()

@@

hell.plot

The Hellinger distances reveal that

```{r densityplots, warning=FALSE, message=FALSE, echo=FALSE, fig.height = 10, fig.width=7}

source('R/figures//ordination_plot.R')
ordi_plot

When we examine the taxa seperately we can see that by far the majority of comparisons show greater differences due to climate change than due to shifts in distribution:

This plot makes it clear that precipitation across the region has changed significantly since the PLS era (or the early 1900s), while overall $t_{mean}$ has changed less.  Among taxa only beech, ironwood, hemlock, fir and tamarak show distributional changes larger than the effect of shifting climate.  For beech, a shift is seen in $t_{mean}$, where $t_{mean}$ for the PLS era distribution is 6.8^o^C, but is lower for the FIA distribution using PLS era climate, at $t_{mean}$ = 6.6^o^C.  This is likely due to a northward shift in beech distribution in the current FIA dataset due to the loss of southern beech forests (earlier Figure).

>>>>

source('R/Setup_R.R')
source('R/load_climate.R') # gives `climate` with elements `then`, `now` and `names`
source('R/load_veg.R')

@@

#  This takes a bit of time.
loss_plots <- loss_plot()

@@

#  Returns a list with the ggplot (object 1) and all.hellinger.
hell_plot <- hellinger_plot()

```
**Figure X**. *For each of the four variables examined we see*

The Hellinger distances reveal that while taxa may show the imprint of land use change on shifting climatic niches, this shift is not uniform across taxa not climatic  variables. Maximum temperature shows the greatest change attributed to land use change.  Tamarack, elm, poplar, spruce beech, cedar, and fir all show a greater influence for land use change than regional climate change.

The precipitation panel (Figure X) indicates that precipitation across the region has driven change in the species climate niche for this variable.  Only spruce and poplar show a marginally greater effect of land use change than climate change, wheras taxa such as beech and hemlock show a strong climate signal.

Interstingly, since the pre-settlement era maximum temperatures have declined, while minimum temperatures have increased strongly.
